\textls[-0]{\thetitle}

### 2023-03-16 canonicitymodel.tex
Save Canonicity Model.

\newcommand{\GTy}[2]{\ensuremath{\Glued{\texttt{Ty}}_{#1}~{#2}}}
\newcommand{\GCon}[1]{\ensuremath{\Glued{\texttt{Con}}_{#1}}}
\newcommand{\GMWSig}[3]{\ensuremath{{\texttt{WSig}^C}_{#1}^{#3}~{#2}}}
\newcommand{\GWSig}[3]{\ensuremath{{\Glued{\texttt{WSig}}}_{#1}^{#3}~{#2}}}

There are actually more \emph{internal} type-theoretic construction to explore, and we need them to define the model for \TT as well.

@@

and $\GTy{j}{\Glued{\Gm}} \coloneq \sum_{\goodType{\Gm}{T}{j}} \prod_{\goodSub{\cdot}{\gm}{\Gm}}\prod_{\gm' \in \Gmodel{\Glued{\Gm}}(\gm)}\{t : \goodTerm{\cdot}{t}{\sub{T}{\gm}}\}\to\Set{j} $ for $\Glued{\Gm} \in \GCon{k}$.

Basically the point is, for each well-typed type $\goodType{\Gm}{T}{j}$,  we have its denotation $\denotesCC{T} \in \GTy{j}{\denotesCC{\Gm}}$.

@@

@@

together with the following inductively defined indexed set and its eliminator principle. These can be directly translated into Agda but we use a more conventional math notation
  "Inductive"~CW_p : (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    "CWsup"_p : n < N \to 

>>>>

\newcommand{\GTy}[2]{\ensuremath{\Glued{\texttt{Ty}}_{#1}~{#2}}}
\newcommand{\GCon}[1]{\ensuremath{\Glued{\texttt{Con}}_{#1}}}
\newcommand{\GTm}[2]{\ensuremath{\Glued{\texttt{Tm}}~{#1}~{#2}}}
\newcommand{\GMWSig}[3]{\ensuremath{{\texttt{WSig}^C}_{#1}^{#3}~{#2}}}
\newcommand{\GWSig}[3]{\ensuremath{{\Glued{\texttt{WSig}}}_{#1}^{#3}~{#2}}}

There are actually more \emph{internal} type-theoretic construction to we need:

@@

and $\GTy{j}{\Glued{\Gm}} \coloneq \sum_{\goodType{\Gm}{T}{j}} \prod_{\goodSub{\cdot}{\gm}{\Gm}}\prod_{\gm' \in \Gmodel{\Glued{\Gm}}(\gm)}\{t : \goodTerm{\cdot}{t}{\sub{T}{\gm}}\}\to\Set{j} $ for $\Glued{\Gm} \in \GCon{k}$

and $\GTm{\Glued{\Gm}}{\Glued{T}} \coloneq \sum_{\goodTerm{\Gm}{t}{T}} \prod_{\goodSub{\cdot}{\gm}{\Gm}} \prod_{\gm' \in\Gmodel{\Glued{\Gm}}} \Gmodel{\Glued{T}}(\gm)(\gm')(\sub{t}{\gm})$

Basically the point is, for each well-typed type $\goodType{\Gm}{T}{j}$,  we have its denotation $\denotesCC{T} \in \GTy{j}{\denotesCC{\Gm}}$; and for each well-typed term $\goodTerm{\Gm}{t}{T}$, we have its denotation $\denotesCC{t} \in \GTm{\denotesCC{\Gm}}{\denotesCC{T}}$. Bascially the four sets are collecting the glued interpretation.

@@

\newcommand{\CWmodel}{\ensuremath{\mathit{W}^C}}
\newcommand{\CWsup}{\ensuremath{\mathit{Wsup}^C}}
\newcommand{\CWrec}{\ensuremath{\mathit{Wrec}^C}}

@@

together and mutual recursively defined with the following inductively defined indexed set $\CWmodel$ (with only one constructor $\CWsup$) ....

\begin{align*}
  "Inductive"~\CWmodel &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    \CWsup &: j < N \to \Glued{a} \in \GTm{\Glued{\cdot}}{\wsigproj{j}{1}{\Glued{\wsig}}} \\
    & \to \Glued{b} \in (\GTm{(\Glued{\cdot} \Glued{,} \sub{\wsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\SubstId}{\Glued{a}}}) }{\sub{\El{\wcode{\wsig}}}{\SubstWeak{1}}}) \to \CWmodel~\Glued{\wsig}~\Wsup{j}{\wsig}{a}{b}
\end{align*}
... and its eliminator principle $\CWrec$. 
\begin{align*}
  \CWrec &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to 
    (P : \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{k})  \\
    & \to [j < N \to  \Glued{a} \in \GTm{\Glued{\cdot}}{\wsigproj{j}{1}{\Glued{\wsig}}} \\ 
    & \quad \quad \to 
    b \in (\GTm{({\cdot} {,} \sub{\wsigproj{j}{2}{{\wsig}}}{\SubstExt{\SubstId}{{a}}}) }{\sub{\El{\wcode{\wsig}}}{\SubstWeak{1}}}) \\ 
    & \quad \quad \to b^C : (\Glued{\gm} \in (\Glued{\cdot} \Glued{,} \sub{\wsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\SubstId}{\Glued{a}}}) \to P~\sub{b}{\Gmodel{\Glued{\gm}}}) \\
    & \quad \quad \to P~(\Wsup{j}{\wsig}{a}{b}) ] \\
    & \to \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \to \CWmodel~\Glued{\wsig}~t \to P~t \\
  \CWrec & \Glued{\wsig}~P~f~t~(\CWsup~\Glued{a}~\Glued{b}) = f~\Glued{a}~b~(\lambda )
\end{align*}

Note that in $\CWmodel$, the $\Glued{b}$ uses the definition of $\denotesC{\wcode{\wsig}}$, which after unfolding, will refers to $\CWmodel$ again and in strictly positive position. So it is a well-founded definition.
